6.867 Problem Set 1

### 2015-12-08 Project/Latex/Paper.tex
[project] some linear regression eval and plots.

\subsubsection{Article Perplexity}

@@

%------------------------------------------------
\phantomsection
\section*{Acknowledgments} % The \section*{} command stops section numbering

>>>>

\subsection{Article Perplexity}

@@

\begin{figure*}[ht]\centering
\includegraphics[width=\linewidth]{feature_weights.png}
\caption{Linear Regression Feature Weights (excluding intercept term)}
\label{fig:lin_reg_weights}
\end{figure*}

\begin{tabular}{lr}
\toprule
Feature  &  Weight\\
\midrule
intercept & 9.047\\
log\_wcount & 0.729\\
desk\_Foreign & 0.657\\
section\_World & -0.553\\
desk\_Travel & -0.472\\
typeOfMaterial\_Schedule & -0.291\\
section\_Movies & -0.277\\
section\_Opinion & 0.261\\
typeOfMaterial\_Review & -0.255\\
desk\_National & 0.253\\
typeOfMaterial\_Letter & -0.243\\
section\_Sports & -0.215\\
section\_Education & -0.199\\
section\_Books & 0.192\\
section\_Corrections & -0.179\\
desk\_Weekend & -0.175\\
section\_Health & 0.172\\
type\_BlogPost & -0.170\\
desk\_BookReview & -0.169\\
typeOfMaterial\_Op-Ed & 0.167\\
\end{tabular}
%------------------------------------------------
\phantomsection
\section*{Acknowledgments} % The \section*{} command stops section numbering
